---
title: COVID-19, Tamil Nadu, Live Update
author: Vignesh A
date: '2020-06-11'
slug: covid-19-tamil-nadu-live-update
categories: []
tags: []
---

```{r,include=FALSE,echo=FALSE,warning=FALSE}
library(rgdal)
library(tidyverse)
library(leaflet)
library(ggplot2)
library(ggrepel)
library(cowplot)
```
```{r,echo=FALSE,warning=FALSE,include=FALSE}
rm(nycounties)
nycounties <- rgdal::readOGR("tamilnadu.json")
csv <- read.csv('district_wise.csv')
dist_daily <- csv %>%
  filter(State_Code == 'TN') %>%
  select(District,Confirmed,Active,Delta_Confirmed,Delta_Recovered)
colnames(dist_daily) <- c('district','Cases','Active','Today','Today_rec')
nycounties <- merge(nycounties,dist_daily,by = 'district')
state_daily <- read.csv('state_wise_daily.csv')
#head(state_daily)

#View(state_daily)
state_daily <- state_daily[,c(1,2,35)]
#names(state_daily)
state_daily$Date <- as.character(state_daily$Date)
state_daily$Date <- as.Date(state_daily$Date, '%d-%b-%y')



```

## **COVID-19 TAMIL NADU** 
(last update : `r Sys.time()`)

## Total Number of cases : **`r state_daily %>%filter(Status =='Confirmed') %>%summarise(sum(TN)) `**

### Total Number of cases in Tamil Nadu - DISTRICT WISE

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
bins1 <- c(0, 50, 100, 200, 300, 400, 500, 1000, 10000,20000,30000,Inf)
pal1 <- colorBin("Reds",domain = nycounties$Cases,bins = bins1)
leaflet(nycounties) %>%
  setView(lng = 78.63, lat = 11.12, zoom = 7) %>%
  #addTiles() %>%
  addPolygons(stroke = TRUE, 
              weight = 2,
              #popup = cat(paste("District:", nycounties$district,'\n',
                           # "Today:", nycounties$Today)), 
              #label = ~cat(nycounties$district,':',nycounties$Case,'\nTotal:',nycounties$Total),
              smoothFactor = 0.3, fillOpacity = 2,
              fillColor = ~pal1(Cases),
              color = "black ", opacity = 10,
              label = ~paste0(district, ": ", formatC(Cases, big.mark = ","),
                              "\n",'Today :',formatC(Today,big.mark = ',')),
              labelOptions = labelOptions(noHide = F, textsize='15px')) %>% 
  addLegend(pal = pal1, values = ~Cases, opacity = 0.7, title = NULL,position = "bottomright")

```

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
state_daily_line <- state_daily %>%
  filter(Status == 'Confirmed',between(Date,Sys.Date()-20,Sys.Date())) %>%
  ggplot(aes(x=Date,y = cumsum(TN))) +
  geom_line(col = "pink",size =2)+
  geom_point(col='red',size = 4)+
  ylab('Number of Cases') +
  xlab('Date') +
  ggtitle("Daywise cases in TN ")+
  #scale_x_continuous(limits = c(2008,2020),
  #                   breaks = seq(from = 2008, to = 2019, by = 1)) + 
  theme_bw()+
  geom_label_repel(aes(label = cumsum(TN)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50')
  
state_daily_bar <- state_daily %>%
  filter(Status == 'Confirmed',between(Date,Sys.Date()-7,Sys.Date())) %>%
  ggplot(aes(x=Date,y=TN)) + 
  geom_bar(fill = 'blue',color ='black',alpha = .4,stat = 'identity',width = 0.4) +
  ylab('Number of Cases') +
  xlab('Date') +
  ggtitle("Number of Cases in last 7 Days ")+
  #scale_x_continuous(limits = c(2008,2020),
   #                  breaks = seq(from = 2008, to = 2019, by = 1)) + 
  scale_x_date(date_breaks = "1 day")+
  theme_bw()+
  geom_label_repel(aes(label = TN),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50')



plot_grid(state_daily_line,state_daily_bar)

```


### Active Cases in Tamil Nadu - District Wise

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
bins <- c(0,10,20, 50, 100, 200,500, 1000, 2000,10000,Inf)
pal <- colorBin("Blues",domain = nycounties$Cases,bins = bins)


leaflet(nycounties) %>%
  setView(lng = 78.63, lat = 11.12, zoom = 7) %>%
  #addTiles() %>%
  addPolygons(stroke = TRUE, 
              weight = 2,
              smoothFactor = 0.3, fillOpacity = 2,
              fillColor = ~pal(Active),
              color = "black ", opacity = 10,
              label = ~paste0(district, ": ", formatC(Active, big.mark = ",")),
              labelOptions = labelOptions(noHide = F, textsize='15px')) %>% 
  addLegend(pal = pal, values = ~Active, opacity = 0.7, title = NULL,position = "bottomright")


```


### Number of People Recovered : **`r state_daily %>%filter(Status == 'Recovered') %>%summarise(sum(TN))` **

```{r,echo=FALSE,warning=FALSE}

state_daily %>%
  filter(Status == 'Recovered',between(Date,Sys.Date()-7,Sys.Date())) %>%
  ggplot(aes(x=Date,y=TN)) + 
  geom_bar(fill = 'green',color ='black',alpha = .4,stat = 'identity',width = 0.4) +
  ylab('Number of Recovery') +
  xlab('Date') +
  ggtitle("Number of Recovery in last 7 Days ")+
  #scale_x_continuous(limits = c(2008,2020),
  #                  breaks = seq(from = 2008, to = 2019, by = 1)) + 
  scale_x_date(date_breaks = "1 day")+
  theme_bw()+
  geom_label_repel(aes(label = TN),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50')

```


### TOTAL NUMBER OF DECEASED : **`r state_daily %>%filter(Status == 'Deceased') %>%summarise(sum(TN))`**

```{r,echo=FALSE,warning=FALSE}
state_daily %>%
  filter(Status == 'Deceased',between(Date,Sys.Date()-7,Sys.Date())) %>%
  ggplot(aes(x=Date,y=TN)) + 
  geom_bar(fill = 'red',color ='black',alpha = .4,stat = 'identity',width = 0.4) +
  ylab('Number of Deceased') +
  xlab('Date') +
  ggtitle("Number of Deceased in last 7 Days ")+
  #scale_x_continuous(limits = c(2008,2020),
  #                  breaks = seq(from = 2008, to = 2019, by = 1)) + 
  scale_x_date(date_breaks = "1 day")+
  theme_bw()+
  geom_label_repel(aes(label = TN),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50')
```




