---
title: COVID-19, India, Live Update
author: Vignesh A
date: '2020-08-23'
slug: covid-19-india-live-update
categories: ["COVID-19 Dashboard",'R']
tags: []
---
```{r,include=FALSE,echo=FALSE,warning=FALSE}
library(xts)
library(dygraphs)
library(plotly)
library(scales)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(leaflet)
library(dygraphs)
library(magrittr)
```

**COVID-19 affects different people in different ways. Most infected people will develop mild to moderate illness and recover without hospitalization.**

Most common symptoms:

1. fever
2. dry cough
3. tiredness
4. Less common symptoms
5. aches and pains
6. sore throat
7. diarrhoea
8. conjunctivitis
9. headache
10. loss of taste or smell
11. a rash on skin, or discolouration of fingers or toes


For informational purposes only. Consult your local medical authority for advice.

```{r,,include=FALSE,echo=FALSE,warning=FALSE}
dyCSScool <- function(dygraph){
  
  dygraph$x$css <- '
  .dygraph-legend {
  width: auto !important;
  min-width: 150px;
  color: white;
  background-color: #BABABA !important;
  padding-left:5px;
  border-color:#BABABA;
  border-style:solid;
  border-width:thin;
  transition:0s 4s;
  z-index: 80 !important;
  box-shadow: 2px 2px 5px rgba(0, 0, 0, .3);
  border-radius: 3px;
  }
  
  .dygraph-legend:hover{
  transform: translate(-110%);
  transition: 0s;
  }
  
  .dygraph-legend > span {
  color: black;
  padding-left:5px;
  padding-right:2px;
  margin-left:-5px;
  background-color: white !important;
  display: block;
  }
  
  .dygraph-legend > span:first-child {
  margin-top:2px;
  }
  
  .dygraph-legend > span > span{
  display: inline;
  }
  
  .highlight {
  border-left: 2px solid #BABABA;
  padding-left:3px !important;
  }
  '
  dygraph
}

```






```{r,echo=FALSE,warning=FALSE,include=FALSE}
test <- read.csv('https://api.covid19india.org/csv/latest/state_wise.csv')
colnames(test) <- c("ST_NM","Confirmed","Recovered","Deaths" ,"Active","Last_Updated_Time"
                    ,"Migrated_Other"  ,  "State_code"  ,      "Delta_Confirmed"  
                    ,"Delta_Recovered"  , "Delta_Deaths",      "State_Notes")
nycounties <- rgdal::readOGR("india_states.geojson")
test$ST_NM <- as.character(test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Jammu and Kashmir',"Jammu & Kashmir",test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Dadra and Nagar Haveli and Daman and Diu',"Daman & Diu",test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Andaman and Nicobar Islands',"Andaman & Nicobar Island",test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Delhi',"NCT of Delhi",test$ST_NM)


india <- sp::merge(nycounties,test,by = 'ST_NM')
bins <- c( 0,500,600,700,800,900, 1000, 2000,3000,4000,5000,6000,7000,8000,10000,15000,20000,25000,30000,Inf)
pal1 <- colorBin("Reds",domain = nycounties$Cases,bins = bins)
labels <- sprintf(
  '<strong>%s</strong><br/>
  <b>Total Cases</b>:<b style="color:#F70D1A">%g</b><br/>
  <b>Today:</b> <b style="color:#F70D1A">+ %g </b><br/>
  <b>Active :</b> <b style="color:#F70D1A">%g</b><br/>
  <b>Death :</b> <b style="color:#F70D1A">%g</b> ',
  india$ST_NM, india$Confirmed, india$Delta_Confirmed,india$Active,india$Deaths
) %>% 
  lapply(htmltools::HTML)



```

# COVID-19 INDIA LIVE UPDATE
Last Update : `r Sys.time()`

### Number Of cases in India : **`r test %>% filter(ST_NM == 'Total') %>%select(Confirmed)`**
Today : **+`r test %>% filter(ST_NM == 'Total') %>%select(Delta_Confirmed)` **


### Number of Active Cases : **`r test %>% filter(ST_NM == 'Total') %>%select(Active)`**


### Number of Recovered : **`r test %>% filter(ST_NM == 'Total') %>%select(Recovered)`**
Today : **+`r test %>% filter(ST_NM == 'Total') %>%select(Delta_Recovered)`**


### Number of Deceased : **`r test %>% filter(ST_NM == 'Total') %>%select(Deaths)`**
 Today : **+`r test %>% filter(ST_NM == 'Total') %>%select(Delta_Deaths)`**

## STATE-WISE

```{r,echo=FALSE,warning=FALSE}
leaflet(india) %>%
  setView(lng = 78.96, lat = 20.59, zoom = 4) %>%
  addPolygons(stroke = TRUE, 
              weight = 2,
              smoothFactor = 0.3, fillOpacity = 2,
              fillColor = ~pal1(Active),
              color = "black ", opacity = 10,
              label = labels,
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           fillOpacity = 0.3,
                                           bringToFront = TRUE),
              labelOptions = labelOptions(noHide = F, textsize='15px'))
```

```{r,echo=FALSE,warning=FALSE}
knitr::kable(test[-1,c("ST_NM","Confirmed","Recovered","Active","Deaths" )])
```




## Conformed cases day wise.


```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}
india_daily <- read.csv('https://api.covid19india.org/csv/latest/state_wise_daily.csv')

india_daily <- india_daily[,c(1,3,4)]


india_daily$Date <- as.Date(india_daily$Date, '%d-%b-%y')
cnf <- india_daily %>% 
  filter(Status == "Confirmed") %>%
  select(Date,TT)

rec <- india_daily %>% 
  filter(Status == "Recovered") %>%
  select(Date,TT)
dec <- india_daily %>% 
  filter(Status == "Deceased" ) %>%
  select(Date,TT)

crd <- cbind(cnf,rec,dec)

crd <- crd[,c(1,2,4,6)]
names(crd) <- c('Date','Confirmed','Recovered','Deceased')
cumsum_crd <- crd %>%
  mutate(TotalC = cumsum(Confirmed),TotalR = cumsum(Recovered),
         TotalD = cumsum(Deceased)) 

dygraph(xts(cumsum_crd[,c(2,5)],order.by = cumsum_crd$Date)) %>%
  dySeries("TotalC",drawPoints = TRUE,pointSize = 3, label = "Total Confirmed",color = 'red') %>%
  dySeries("Confirmed",label = "Today",color = '#000000', stepPlot = TRUE, fillGraph = TRUE) %>%
  dyOptions(stackedGraph = FALSE,
            fillGraph = TRUE,
            drawPoints = TRUE,
            pointSize = 3,
            mobileDisableYTouch = TRUE) %>%
  dyRangeSelector(dateWindow = c(cumsum_crd$Date[length(cumsum_crd$Date)]-20,
                                 cumsum_crd$Date[length(cumsum_crd$Date)])) %>%
  dyCSScool() %>%
  dyLegend(show = 'follow')

```
* Adjust the date slider for data between particular dates *

## Active cases day Wise (Cumulative)

```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}
df <- read.csv('https://api.covid19india.org/csv/latest/state_wise_daily.csv')
date <- unique(df$Date)
rm(act1)
rm(dat1)
act1 <- NULL
dat1 <- NULL
dat1 <- unique(df$Date)

for(i in 1:length(date)){
  act1[i] <- as.numeric(df %>% 
                         filter(Date == date[i]) %>% 
                         select(Status,Date,TT) %>%
                         mutate(Active = TT[1] - TT[2]-TT[3]) %>%
                         select(Active) %>%
                         unique())
}

active <- cbind(as.data.frame(dat1),as.data.frame(act1))
active$dat1 <- as.Date(active$dat1,'%d-%b-%y')
active <- as.data.frame(active %>%
                          mutate(cumsum = cumsum(act1)))

dygraph(xts(active$cumsum,order.by = active$dat1)) %>%
  dySeries(drawPoints = TRUE,pointSize = 3, label = "Total active",color = 'blue') %>%
  dyOptions(stackedGraph = FALSE,
            fillGraph = TRUE,
            drawPoints = TRUE,
            pointSize = 3,
            mobileDisableYTouch = TRUE) %>%
  dyRangeSelector(dateWindow = c(active$dat1[length(active$dat1)]-80,
                                 active$dat1[length(active$dat1)])) %>%
  dyCSScool() %>%
  dyLegend(show = 'follow')

```








## Recovered cases day wise


```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}

dygraph(xts(cumsum_crd[,c(3,6)],order.by = cumsum_crd$Date)) %>%
  dySeries("TotalR",drawPoints = TRUE,pointSize = 3, label = "Total Recovered",color = 'Green') %>%
  dySeries("Recovered",label = "Today",color = '#000000', stepPlot = TRUE, fillGraph = TRUE) %>%
  dyOptions(stackedGraph = FALSE,
            fillGraph = TRUE,
            drawPoints = TRUE,
            pointSize = 3,
            mobileDisableYTouch = TRUE) %>%
  dyRangeSelector(dateWindow = c(cumsum_crd$Date[length(cumsum_crd$Date)]-20,
                                 cumsum_crd$Date[length(cumsum_crd$Date)])) %>%
  dyCSScool() %>%
  dyLegend(show = 'follow')
```

* Adjust the date slider for data between particular dates *


## Deceased Day-wise


```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}

dygraph(xts(cumsum_crd[,c(4,7)],order.by = cumsum_crd$Date)) %>%
  dySeries("TotalD",drawPoints = TRUE,pointSize = 3, label = "Total Deceased",color = '#808080') %>%
  dySeries("Deceased",label = "Today",color = '#000000', stepPlot = TRUE, fillGraph = TRUE) %>%
  dyOptions(stackedGraph = FALSE,
            fillGraph = TRUE,
            drawPoints = TRUE,
            pointSize = 3,
            drawGapEdgePoints = TRUE,
            mobileDisableYTouch = TRUE) %>%
  dyRangeSelector(dateWindow = c(cumsum_crd$Date[length(cumsum_crd$Date)]-20,
                                 cumsum_crd$Date[length(cumsum_crd$Date)])) %>%
  dyCSScool()%>%
  dyLegend(show = 'follow')
```

* Adjust the date slider for data between particular dates *
