---
title: Classification, Part - 2, Multinominal logistic Regression.
author: Vignesh A
date: '2020-05-23'
slug: classification-part-2-multinominal-logistic-regression
categories: []
tags: []
---

```{r,include=FALSE,echo=FALSE,warning=FALSE}
library(tidyverse)
library(caret)
library(nnet)

```


This will eb small Post, we will be discusing about Multinominal Logistic Regression, When the predicted i.e when dependent variable has multiple category.    

We will be using the  famous **iris** dataset

The dataset consist of columns:
```{r,echo=FALSE,warning=FALSE}
names(iris)
```

```{r,echo=FALSE,warning=FALSE}
str(iris)
```

We can see, we arte trying to predict Species, which has 3 factors.

We will be creating training and test set


```{r,echo=FALSE,warning=FALSE}
#data("iris")

# Inspect the data
#sample_n(iris, 3)
#iris %>%
 # count(Species)
#count(iris$Species)
# Split the data into training and test set
set.seed(123)
training.samples <- iris$Species %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- iris[training.samples, ]
test.data <- iris[-training.samples, ]
cat("Training set has",dim(train.data)[1], 'entries')
cat("Testing set has",dim(test.data)[1] ,'entries')
```

# Model Creation

Now, we will be creating the model with our training data.

```{r,echo=FALSE,warning=FALSE}
model <- nnet::multinom(Species ~., data = train.data)
# Summarize the model
summary(model)

```

And We will test the model, on our testing data adn we will find the accuracy of our model.

The Accuracy of our Model is

```{r,echo=FALSE,warning=FALSE}
predicted.classes <- model %>% predict(test.data)
#head(predicted.classes)
# Model accuracy
mean(predicted.classes == test.data$Species)
```

This is just a basic model, we will be analyse this in detail in upcoming post.

# Thank You