---
title: Crime Against Womens in India
author: Vignesh A
date: '2020-06-01'
slug: crime-against-womens-in-india
categories: []
tags: []
---

```{r,include=FALSE,echo=FALSE,warning=FALSE}
library(Amelia)
#missmap(df)
library(tidyverse)
#names(df)
library(ggplot2)
#unique(df$STATE.UT)
library(tidyverse)
library(ggrepel)
library(cowplot)
library(dplyr)
library(plotly)
library(rjson)
```

# Cases Against Womens In India

# *Key Findings*

* *4 Rape cases were filed per hour in India*
* *13 Cruelty by Husband or his Relatives per hour in India*
* *Average Number of crimes Against women per year is : 194586*
* *41% cases are classified under "Cruelty by Husband or his Relatives"*


In this discriptive analysis we will be looking into CRime Against Womens that are filed dataset from [data.gov.in](https://data.gov.in/).

This data type consist of different types of complains against womens in India from 2001 to 2015.

```{r,echo=FALSE,warning=FALSE}
df <- read.csv('datasets_423357_807380_crimes_against_women_2001-2014.csv')
#back_df <- df
#names(df)
df <-df[,-1]
#head(df,2)
#colnames(df)
#dim(df)
df15 <- read.csv('District-wise_Crimes_committed_against_Women_2015_1(1).csv')
colnames(df15) <- colnames(df)
#colnames(df15)
df <- rbind(df,df15)

```
Columns in dataset:
```{r,echo=FALSE,warning=FALSE}
names(df)
```

From Above we can see the cases against womens are classifier under 7 Categories.

1. Rape
2. Kidnapping and Abduction
3. Dowry Deaths
4. Assault on women with intent to outrage her modesty
5. Insult to modesty of Women
6. Cruelty by Husband or his Relatives
7. Importation of Girls

```{r,echo=FALSE,warning=FALSE}
df$Year <- factor(df$Year)
#str(df$Year)

df$STATE.UT <- tolower(df$STATE.UT) 
#str(df)
#unique(df$STATE.UT)
df$STATE.UT <- ifelse(df$STATE.UT == 'd&n haveli',"d & n haveli",df$STATE.UT)
df$STATE.UT <- ifelse(df$STATE.UT == 'a&n islands',"a & n islands",df$STATE.UT)
df$STATE.UT <- ifelse(df$STATE.UT == 'delhi ut',"delhi",df$STATE.UT)
#unique(df$STATE.UT)
df$DISTRICT <- tolower(df$DISTRICT)
df$DISTRICT <- ifelse(df$DISTRICT == 'zz total',"total",df$DISTRICT)
df$DISTRICT <- ifelse(df$DISTRICT == 'total district(s)',"total",df$DISTRICT)
#Total District(s)
#unique(df$DISTRICT)
#ZZ TOTAL
#state_list <- as.list(unique(df$STATE.UT))
#df <- as.table(df)
#data <- read.table(text = df,header=TRUE)
#split(df,df$STATE.UT)[1]
#df$Year <- as.integer(df$Year)


#########################################################################

Total_case <- df %>%
  filter(DISTRICT == 'total') %>% 
  group_by(Year) %>%
  summarise(sum(Rape,Kidnapping.and.Abduction,Dowry.Deaths,
                Assault.on.women.with.intent.to.outrage.her.modesty,
                Insult.to.modesty.of.Women,
                Cruelty.by.Husband.or.his.Relatives,
                Importation.of.Girls))

colnames(Total_case) <- c('Year','Cases')


```



The *Total Number Of cases Filed against womens in India between 2001 to 2015* : **`r sum(Total_case$Cases)`**

Average Number of cases per year is : **194586**

# Cases Filled Year-Wise

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}


total_bar <- ggplot(Total_case,aes(x = Year,y=Cases)) + 
    geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,320000),
                     breaks = seq(from = 0, to = 320000, by = 50000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Cases,label = Cases),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Cases Filled between 2001 and 2015 in INDIA')

Total_case <- Total_case %>%
  mutate(cumsum = cumsum(Cases))
####################################################################
total_line <- ggplot(Total_case,aes(x = Year,y=cumsum(Cases),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,3000000),
                     breaks = seq(from = 0, to = 3000000, by = 500000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum,label = cumsum),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Cases Filled between 2001 and 2015 in INDIA')



plot_grid(total_line,total_bar)

```

* Line Chart indiacates aggregated number of cases over the years. We can see that the rate of increase has been increased and reducing.

* Bar Graph shows the number of cases per year, which clearly hows that has been increasing over the years. 

* Number of cases Filed in 2015 is **More Than Twice the cases Files in 2001**.
* Maximum Number of cases were filed on **2014 with 317361 Cases**

* Minimum Number of cases were filed on **2001 with 128537 Cases**     

# NUMBER OF CASES, STATE WISE.

The Below Map will give us a clear picture about the number of cases per State in India

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=12,out.width='100%'}
state_map <- as.data.frame(df %>%
                             filter(DISTRICT == 'total') %>% 
                             group_by(STATE.UT) %>%
                             summarise(sum(Rape,Kidnapping.and.Abduction,Dowry.Deaths,
                                           Assault.on.women.with.intent.to.outrage.her.modesty,
                                           Insult.to.modesty.of.Women,
                                           Cruelty.by.Husband.or.his.Relatives,
                                           Importation.of.Girls)))
state_map$STATE.UT <- toupper(state_map$STATE.UT)  
state_map$STATE.UT <- ifelse(state_map$STATE.UT == 'A & N ISLANDS',
                             'ANDAMAN & NICOBAR ISLAND',
                             state_map$STATE.UT)
state_map$STATE.UT <- ifelse(state_map$STATE.UT == 'D & N HAVELI',
                             'DADARA & NAGAR HAVELLI',
                             state_map$STATE.UT)
state_map$STATE.UT <- ifelse(state_map$STATE.UT == 'DELHI',
                             'NCT OF DELHI',
                             state_map$STATE.UT)
state_map <- state_map[order(state_map$STATE.UT),]
rm(xy)
rm(x)
rm(y)
x <- as.character()
y <- as.character()
geojson <- rjson::fromJSON(file = 'states_india.geojson')
for(i in 1:length(geojson$features)){
  x[i] <-  geojson$features[[i]]$properties$state_code
  y[i] <-  geojson$features[[i]]$properties$st_nm
} 

xy <- data.frame(x,y)
xy$y <- toupper(xy$y)
xy <- xy[order(xy$y),]
state_map <-cbind(state_map,xy$x)
geojson <- rjson::fromJSON(file = 'states_india.geojson')
g <- list(
  fitbounds = "locations",
  visible = FALSE
)
fig1 <- plot_ly() 
fig1 <- fig1 %>% add_trace(
  type="choropleth",
  geojson=geojson,
  locations=state_map$`xy$x`,
  z=state_map$`sum(...)`,
  colorscale="OrRd",
  featureidkey="properties.state_code",
  text = state_map$STATE.UT
)
fig1 <- fig1 %>% layout(
  geo = g
)
fig1 <- fig1 %>% colorbar(title = "Number Of Case")
fig1 <- fig1 %>% layout(
  title = "Total Cases Filed Statewise India 2001-2015"
)
fig1

```


* The Maximum Number of cases are from **Uttar Pradesh** followed by **Andra Pradesh and West Bengal**.

* **Nagalaya** has the minimum number of cased followed by **Sikkim**

* The Cental States have a higher number of cases when compared to other parts of India.


Now we will seeing how the cases are categorised.
```{r,echo=FALSE,warning=FALSE}
india_ind_case <- as.data.frame(df %>%
                                  filter(DISTRICT == 'total')  %>%
                                  #group_by(STATE.UT) %>%
                                  summarise(Rape = sum(Rape),
                                            Kidnapping.and.Abduction = sum(Kidnapping.and.Abduction),
                                            Dowry.Deaths = sum(Dowry.Deaths),
                                            Assault.on.women.with.intent.to.outrage.her.modesty = sum(Assault.on.women.with.intent.to.outrage.her.modesty),
                                            Insult.to.modesty.of.Women = sum(Insult.to.modesty.of.Women),
                                            Cruelty.by.Husband.or.his.Relatives = sum(Cruelty.by.Husband.or.his.Relatives),
                                            Importation.of.Girls = sum(Importation.of.Girls)) %>%
                                  t())
#names(india_ind_case)
india_ind_case$Case <- rownames(india_ind_case)
#colnames(india_ind_case) <- c('Case','Total')
#colnames(india_ind_case)

#library(highcharter)
rownames(india_ind_case) <- NULL
colnames(india_ind_case) <- c('Total','Case')

#install.packages("ggpubr")
#india_ind_case
#View(india_ind_case)
#names(india_ind_case)
#library(ggpubr)
#library(plotly)
fig <- plot_ly(india_ind_case, labels = ~Case, values = ~Total, type = 'pie')
fig <- fig %>% layout(title = 'Types Of Cases Againt Womens ')

fig
```

* We can see that more than **41%** cases are classified under **Cruelty by Husband or his Relatives**, followed by **Assault on women with intent to outrage her modesty** with **23.3%**.
* **Importation of Womens and Dowry Death** Hold the bottem Position of the tabel with **0.32% and 3.9%** respectively.

## NOW, We will be analysis each category separately.

# Rape

The below graphs will give a clear understanding of Number of Rape Cases Over the years.

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
year_ind <- as.data.frame(df %>%
                            filter(DISTRICT == 'total') %>%
                            group_by(Year) %>% 
                            summarise(Rape = sum(Rape),
                                      Kidnapping.and.Abduction = sum(Kidnapping.and.Abduction),
                                      Dowry.Deaths = sum(Dowry.Deaths),
                                      Assault.on.women.with.intent.to.outrage.her.modesty = sum(Assault.on.women.with.intent.to.outrage.her.modesty),
                                      Insult.to.modesty.of.Women = sum(Insult.to.modesty.of.Women),
                                      Cruelty.by.Husband.or.his.Relatives = sum(Cruelty.by.Husband.or.his.Relatives),
                                      Importation.of.Girls = sum(Importation.of.Girls)))

#############################rape########################################
Rape_bar <- ggplot(year_ind,aes(x = Year,y=Rape)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,40000),
                     breaks = seq(from = 0, to = 40000, by = 8000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Rape,label = Rape),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Rape Cases Filed') +
  ggtitle('Number of Rape Cases Filled each Year in INDIA')
year_ind <- as.data.frame(year_ind %>%
                            mutate(Rape_cumsum = cumsum(Rape)))

Rape_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Rape),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,400000),
                     breaks = seq(from = 0, to = 400000, by = 80000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Rape_cumsum,label = Rape_cumsum),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Rape Cases Filed') +
  ggtitle('Number of Rape Cases Filled between 2001 and 2015 in INDIA')

rm(yr_rp_pr_hr)
year <- numeric()
Per_hour <- numeric()


for(i in 1:dim(year_ind)[1]){
  year[i] <- as.character(year_ind$Year[i])
  Per_hour[i] <- year_ind$Rape[i]/8760
}
yr_rp_pr_hr <- data.frame(year,Per_hour)
yr_rp_pr_hr$Per_hour <- as.numeric(yr_rp_pr_hr$Per_hour)

  
plot_grid(Rape_bar,Rape_line)

```

* Bar Graph indicates that the cases per year keeps on increasing, **when compared to 2001 the number of cases in 2015 increased more than twice**.

* Maximum number of Rape cases were filed in the year 2014, **36735** cases were filed. 

* Minimum Number of Rape cases were filed in 2003 with **15357**.

* Line chart indicates, this is increasing at an alarming rate with year. From 2010 to 2015 the number of cases have almost doubled.

# Number Of Rape Cases Filed Per Hour In India Over Years.

```{r,echo=FALSE,warning=FALSE}
ggplot(yr_rp_pr_hr,aes(x = year,y=round(Per_hour,3))) + 
  geom_bar(stat = 'identity',fill = "light blue",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,5),
                     breaks = seq(from = 0, to = 5, by = 0.5),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = year,y = round(Per_hour,3),label = round(Per_hour,3)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Rape Cases Filed') +
  ggtitle('Number of Rape Cases Filled per HOUR ')

```

We can see the number Rape of cases filed per year, in each year.     

* We can see that in **2015**, around **4** cases were filed per hour, all over india.

* in 2014 , more than 4 Rape cases were filed.

# Kidnapping and Abduction

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
KA_bar <- ggplot(year_ind,aes(x = Year,y=Kidnapping.and.Abduction)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,60000),
                     breaks = seq(from = 0, to = 60000, by = 10000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Kidnapping.and.Abduction,label = Kidnapping.and.Abduction),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of  Cases Filed') +
  ggtitle('Number of Kidnapping and Abduction Cases Filled each Year in INDIA')
#year_ind <- as.data.frame(year_ind %>%
                            #mutate(Rape_cumsum = cumsum(Rape)))
#cumsum(year_ind$Kidnapping.and.Abduction)

KA_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Kidnapping.and.Abduction),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,420000),
                     breaks = seq(from = 0, to = 4200000, by = 80000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum(Kidnapping.and.Abduction),label = cumsum(Kidnapping.and.Abduction)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Kidnapping and Abduction Cases Filled between 2001 and 2015 in INDIA')


plot_grid(KA_bar,KA_line)

```

* There is a steap increse in the Number of Kidnapping and Abduction Cases Filled between 2001 and 2015. 

* from around **1.5 lak in 2010 to more than 4 lak in 2015**, greater than 2 times cases over a period of 5 years 


# Dowry Deaths

```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
DD_bar <- ggplot(year_ind,aes(x = Year,y=Dowry.Deaths)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,9000),
                     breaks = seq(from = 0, to = 9000, by = 2000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Dowry.Deaths,label = Dowry.Deaths),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Dowry Death Cases Filled each Year in INDIA')
#year_ind <- as.data.frame(year_ind %>%
#mutate(Rape_cumsum = cumsum(Rape)))
#cumsum(year_ind$Dowry.Deaths)

DD_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Dowry.Deaths),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,120000),
                     breaks = seq(from = 0, to = 1200000, by = 30000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum(Dowry.Deaths),label = cumsum(Dowry.Deaths)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Dowry Death Cases Filled between 2001 and 2015 in INDIA')


plot_grid(DD_bar,DD_line)

```


* From The Graph we can see that Dowry Death has been **more or less constant over** the years, since many laws has been implemented it still remains the same.


# Assault on women with intent to outrage her modesty


```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
AW_bar <- ggplot(year_ind,aes(x = Year,y=Assault.on.women.with.intent.to.outrage.her.modesty)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,85000),
                     breaks = seq(from = 0, to = 85000, by = 12000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Assault.on.women.with.intent.to.outrage.her.modesty,label = Assault.on.women.with.intent.to.outrage.her.modesty),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Assault on women Cases Filled each Year in INDIA')
#year_ind <- as.data.frame(year_ind %>%
#mutate(Rape_cumsum = cumsum(Rape)))
#cumsum(year_ind$Assault.on.women.with.intent.to.outrage.her.modesty)

AW_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Assault.on.women.with.intent.to.outrage.her.modesty),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,700000),
                     breaks = seq(from = 0, to = 700000, by = 120000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum(Assault.on.women.with.intent.to.outrage.her.modesty),label = cumsum(Assault.on.women.with.intent.to.outrage.her.modesty)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Assault on women Cases Filled between 2001 and 2015 in INDIA')


plot_grid(AW_bar,AW_line)

```

* We can see there was a sudden increase in the number of cases **after 2012**, and the trend been continuing.

* It should be noted that **Sexual Harassment of Women at Workplace (Po. evention, Prohibition and Redressal) Act, 2013** passed in 2013.

# Insult to modesty of Women



```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
###############################Insult.to.modesty.of.Women
#names(year_ind)
#year_ind$Insult.to.modesty.of.Women
AW_bar <- ggplot(year_ind,aes(x = Year,y=Insult.to.modesty.of.Women)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,14000),
                     breaks = seq(from = 0, to = 14000, by = 2500),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Insult.to.modesty.of.Women,label = Insult.to.modesty.of.Women),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Insult to modesty of Women Cases Filled each Year in INDIA')
#year_ind <- as.data.frame(year_ind %>%
#mutate(Rape_cumsum = cumsum(Rape)))
#cumsum(year_ind$Insult.to.modesty.of.Women)

AW_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Insult.to.modesty.of.Women),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,160000),
                     breaks = seq(from = 0, to = 160000, by = 30000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum(Insult.to.modesty.of.Women),label = cumsum(Insult.to.modesty.of.Women)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Insult to modesty of Women Cases Filled between 2001 and 2015 in INDIA')


plot_grid(AW_bar,AW_line)
```

* Similar to **Dowry Death**, this graph is also a constant one. With **Steady number of cases** every year.


# Cruelty by Husband or his Relatives



```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
################################Cruelty.by.Husband.or.his.Relatives

#names(year_ind)
#year_ind$Cruelty.by.Husband.or.his.Relatives
HR_bar <- ggplot(year_ind,aes(x = Year,y=Cruelty.by.Husband.or.his.Relatives)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,125000),
                     breaks = seq(from = 0, to = 125000, by = 30000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Cruelty.by.Husband.or.his.Relatives,label = Cruelty.by.Husband.or.his.Relatives),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Cruelty by Husband or his Relatives Cases Filled each Year in INDIA')
#year_ind <- as.data.frame(year_ind %>%
#mutate(Rape_cumsum = cumsum(Rape)))
#cumsum(year_ind$Cruelty.by.Husband.or.his.Relatives)

HR_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Cruelty.by.Husband.or.his.Relatives),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,1300000),
                     breaks = seq(from = 0, to = 1300000, by = 200000),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum(Cruelty.by.Husband.or.his.Relatives),label = cumsum(Cruelty.by.Husband.or.his.Relatives)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Cruelty by Husband or his Relatives Cases Filled between 2001 and 2015 in INDIA')


plot_grid(HR_bar,HR_line)



```

* We know from the above pie chat that **41%** of total cases belong to this category.
* After 2005, there is a steady increase in the number of cases till 2015.
* In 2015, The number of **Cruelty by Husband or his Relatives** cases filed across india is **13**

# 


```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
###############################Importation.of.Girls
#names(year_ind)
#year_ind %>%
  #select(Importation.of.Girls,Year)
IG_bar <- ggplot(year_ind,aes(x = Year,y=Importation.of.Girls)) + 
  geom_bar(stat = 'identity',fill = "red",col = 'black',alpha = 0.4) +
  scale_y_continuous(limits = c(0,160),
                     breaks = seq(from = 0, to = 160, by = 30),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = Importation.of.Girls,label = Importation.of.Girls),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Importation of Girls Cases Filled each Year in INDIA')
#year_ind <- as.data.frame(year_ind %>%
#mutate(Rape_cumsum = cumsum(Rape)))
#cumsum(year_ind$Importation.of.Girls)

IG_line <- ggplot(year_ind,aes(x = Year,y=cumsum(Importation.of.Girls),group = 1)) + 
  geom_line(col = "light blue",size =2)+
  geom_point(col='blue',size = 4)+
  scale_y_continuous(limits = c(0,1000),
                     breaks = seq(from = 0, to = 1000, by = 200),
                     labels = scales::comma) + theme_bw()+
  geom_label_repel(aes(x = Year,y = cumsum(Importation.of.Girls),label = cumsum(Importation.of.Girls)),box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +scale_fill_discrete(name = 'Type Of Case') +
  xlab('Year') +
  ylab('Number of Cases Filed') +
  ggtitle('Number of Importation of Girls Cases Filled over 2001-15 in INDIA')


plot_grid(IG_bar,IG_line)

```

* We can see the number of cases filed in this category has been decreasing over the years. and in **2015 only 6** cases were filed under this category.

* The Highest Number of cases were filed in **2005 about 148 cases**.



We cannot come to a conclusing that all these cases were true, But still seeing the number of cases applied, which seems to be very high.


We Will be seeing a depth analysis of case againt womens in Tamil Nadu, District wise in Future post.


# Thank You













