---
title: COVID-19, India, Live Update
author: Vignesh A
date: '2020-06-12'
slug: covid-19-india-live-update
categories: []
tags: []
---
```{r,include=FALSE,echo=FALSE,warning=FALSE}
library(xts)
library(dygraphs)
library(plotly)
library(scales)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(leaflet)
```

```{r,echo=FALSE,warning=FALSE,include=FALSE}
test <- read.csv('https://api.covid19india.org/csv/latest/state_wise.csv')
colnames(test) <- c("ST_NM","Confirmed","Recovered","Deaths" ,"Active","Last_Updated_Time"
                    ,"Migrated_Other"  ,  "State_code"  ,      "Delta_Confirmed"  
                    ,"Delta_Recovered"  , "Delta_Deaths",      "State_Notes")
nycounties <- rgdal::readOGR("india_states.geojson")
test$ST_NM <- as.character(test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Jammu and Kashmir',"Jammu & Kashmir",test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Dadra and Nagar Haveli and Daman and Diu',"Daman & Diu",test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Andaman and Nicobar Islands',"Andaman & Nicobar Island",test$ST_NM)
test$ST_NM <- ifelse(test$ST_NM == 'Delhi',"NCT of Delhi",test$ST_NM)


india <- sp::merge(nycounties,test,by = 'ST_NM')
bins <- c( 0,500,600,700,800,900, 1000, 2000,3000,4000,5000,6000,7000,8000,10000,15000,20000,25000,30000,Inf)
pal1 <- colorBin("Reds",domain = nycounties$Cases,bins = bins)
labels <- sprintf(
  '<strong>%s</strong><br/>
  <b>Total Cases</b>:<b style="color:#F70D1A">%g</b><br/>
  <b>Today:</b> <b style="color:#F70D1A">+ %g </b><br/>
  <b>Active :</b> <b style="color:#F70D1A">%g</b><br/>
  <b>Death :</b> <b style="color:#F70D1A">%g</b> ',
  india$ST_NM, india$Confirmed, india$Delta_Confirmed,india$Active,india$Deaths
) %>% 
  lapply(htmltools::HTML)



```

# COVID-19 INDIA LIVE UPDATE
Last Update : `r Sys.time()`

### Number Of cases in India : **`r test %>% filter(ST_NM == 'Total') %>%select(Confirmed)`**
Today : **+`r test %>% filter(ST_NM == 'Total') %>%select(Delta_Confirmed)` **


### Number of Active Cases : **`r test %>% filter(ST_NM == 'Total') %>%select(Active)`**


### Number of Recovered : **`r test %>% filter(ST_NM == 'Total') %>%select(Recovered)`**
Today : **+`r test %>% filter(ST_NM == 'Total') %>%select(Delta_Recovered)`**


### Number of Deceased : **`r test %>% filter(ST_NM == 'Total') %>%select(Deaths)`**
 Today : **+`r test %>% filter(ST_NM == 'Total') %>%select(Delta_Deaths)`**

## STATE-WISE

```{r,echo=FALSE,warning=FALSE}
leaflet(india) %>%
  #setView(lng = 78.96, lat = 20.59, zoom = 4) %>%
  addPolygons(stroke = TRUE, 
              weight = 2,
              smoothFactor = 0.3, fillOpacity = 2,
              fillColor = ~pal1(Active),
              color = "black ", opacity = 10,
              label = labels,
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           fillOpacity = 0.3,
                                           bringToFront = TRUE),
              labelOptions = labelOptions(noHide = F, textsize='15px'))
```

```{r,echo=FALSE,warning=FALSE}
knitr::kable(test[-1,c("ST_NM","Confirmed","Recovered","Active","Deaths" )])
```


```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
india_daily <- read.csv('https://api.covid19india.org/csv/latest/state_wise_daily.csv')

india_daily <- india_daily[,c(1,2,3)]


india_daily$Date <- as.Date(india_daily$Date, '%d-%b-%y')
cnf <- india_daily %>% 
  filter(Status == "Confirmed",between(Date,Sys.Date()-60,Sys.Date()) ) %>%
  select(Date,TT)

rec <- india_daily %>% 
  filter(Status == "Recovered",between(Date,Sys.Date()-60,Sys.Date()) ) %>%
  select(Date,TT)
dec <- india_daily %>% 
  filter(Status == "Deceased",between(Date,Sys.Date()-60,Sys.Date()) ) %>%
  select(Date,TT)

crd <- cbind(cnf,rec,dec)

crd <- crd[,c(1,2,4,6)]
names(crd) <- c('Date','Confirmed','Recovered','Deceased')
dygraph(xts(x = crd[,-1],order.by = crd$Date),
        main = "Confirmed , Recovered and Deceased Count Day-Wise",
        ylab = "Number of cases / Day",
        xlab = 'Date') %>%
  dySeries("Confirmed",drawPoints = TRUE,pointSize = 3, label = "Confirmed",color = 'red') %>%
  dySeries("Recovered",drawPoints = TRUE,pointSize = 3, label = "Recovered",color = 'green') %>%
  dySeries("Deceased",drawPoints = TRUE,pointSize = 3, label = "Deceased") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 40)

```
* Adjust the date slider for data between particular dates *






```{r,echo=FALSE,warning=FALSE,fig.width=12,fig.height=6.5,out.width='100%'}
cumsum_crd <- crd %>%
  mutate(TotalC = cumsum(Confirmed),TotalR = cumsum(Recovered),
         TotalD = cumsum(Deceased)) %>%
  select(Date,TotalC,TotalR,TotalD)

dygraph(xts(x = cumsum_crd[,-1],order.by = cumsum_crd$Date),
        main = "Confirmed , Recovered and Deceased Count",
        ylab = "Number of cases",
        xlab = 'Date') %>%
  dySeries("TotalC",drawPoints = TRUE,pointSize = 3, label = "Confirmed",color = 'red') %>%
  dySeries("TotalR",drawPoints = TRUE,pointSize = 3, label = "Recovered",color = 'green') %>%
  dySeries("TotalD",drawPoints = TRUE,pointSize = 3, label = "Deceased") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 40)

```

* Adjust the date slider for data between particular dates *
