---
title: Whatsapp Chat Data Analysis
author: Vignesh
date: '2020-07-24'
slug: checking-post
categories: ["R"]
tags: []
---
  
# About 
  
  The Whole Idea about this analysis, is to Understand about the persons chatting behavior and finding pattern in Whatsapp Messaging

*In this we will be analysing the chat between two persons*
  
```{r,include=FALSE,echo=FALSE,warning=FALSE}
library(rwhatsapp)
library(lubridate)
library("ggplot2"); theme_set(theme_minimal())
library("lubridate")
library(tidyverse)
library(sqldf)
library(radarchart)
library(plotly)
library(wordcloud)
library(wordcloud2)
library(stopwords)

#Cleanign data for word cloud#

library(SnowballC)
#Creating corpus for word cloud 
library(corpus)
library(tm)
library(ggimage)
library(dygraphs)
library(xts)
library(dplyr)
library(tidyr)


```


```{r,include=FALSE,echo=FALSE,warning=FALSE}
dyCSScool <- function(dygraph){
  
  dygraph$x$css <- '
  .dygraph-legend {
  width: auto !important;
  min-width: 150px;
  color: white;
  background-color: #BABABA !important;
  padding-left:5px;
  border-color:#BABABA;
  border-style:solid;
  border-width:thin;
  transition:0s 4s;
  z-index: 80 !important;
  box-shadow: 2px 2px 5px rgba(0, 0, 0, .3);
  border-radius: 3px;
  }
  
  .dygraph-legend:hover{
  transform: translate(-110%);
  transition: 0s;
  }
  
  .dygraph-legend > span {
  color: black;
  padding-left:5px;
  padding-right:2px;
  margin-left:-5px;
  background-color: white !important;
  display: block;
  }
  
  .dygraph-legend > span:first-child {
  margin-top:2px;
  }
  
  .dygraph-legend > span > span{
  display: inline;
  }
  
  .highlight {
  border-left: 2px solid #BABABA;
  padding-left:3px !important;
  }
  '
  dygraph
}

```




**From the below chart we can clearly see the number of messages sent each day**
  
  
```{r echo=FALSE,warning=FALSE}
chat<- rwa_read('WhatsApp Chat with Sekaru TSM.txt')
whsum <- as.data.frame(chat %>%mutate(day = date(time)) %>%count(day))
colnames(whsum)[2] <- 'No.of.Msg'
dyBarChart <- function(dygraph) {
  dyPlotter(dygraph = dygraph,
            name = "BarChart",
            path = system.file("plotters/barchart.js",
                               package = "dygraphs"))
}

dygraph(xts(whsum$No.of.Msg,order.by = whsum$day)) %>%
  dyBarChart() %>%
  dySeries(drawPoints = TRUE,pointSize = 3, label = "Number Of Messages",color = '#FD7070') %>%
  dyRangeSelector(dateWindow = c(whsum$day[length(whsum$day)]-50,whsum$day[length(whsum$day)])) %>%
  dyCSScool() %>%
  dyLegend(show = 'follow') 
```

```{r echo=FALSE,warning=FALSE}
df<-as.data.frame(chat)
df <- df[,-4]
df <-na.omit(df)
df$day <- weekdays(df$time)
df$date<- as.Date(df$time)
df$hour <-hour(df$time)
#colnames(df)
chat_participants<- as.data.frame(df %>% 
                                    select('author',) %>% 
                                    unique())
#print(paste('total numer of chats : ',count(df)))
```
The Total number of messages were : **`r count(df)`** 
  
  Number of messages sent by each persons:
```{r echo=FALSE,warning=FALSE}
each_auth_no_of_message <- select(df,'author') %>% count(author)
for(i in 1:dim(each_auth_no_of_message)){
  print(paste('Number of messages sent by ',each_auth_no_of_message$author[i],'is',each_auth_no_of_message$n[i]))
}

```



```{r echo=FALSE,warning=FALSE}
count_per_date <- as.data.frame(df %>% 
                                  select(date,day) %>%
                                  count(date) )
count_per_date$day <- weekdays(count_per_date$date)

average_count_per_day <- sqldf("SELECT day,  avg(n) as mean_Y1 FROM count_per_date GROUP BY day")
colnames(average_count_per_day) <- c('Day_of_a_Week','Average_No_of_Msg')
average_count_per_day <- average_count_per_day %>%
  arrange(desc(round(Average_No_of_Msg)))
average_count_per_day$Average_No_of_Msg <-round(average_count_per_day$Average_No_of_Msg)


#head(average_count_per_day,1)

#print(paste('Most number of messages are sent on',average_count_per_day$day[1],'with average of',average_count_per_day$mean[1],'messages'))
```

From the below graph we can able to find the average number of messages sent per day.

```{r echo=FALSE,warning=FALSE}
average_count_per_day$Day_of_a_Week<-ordered(average_count_per_day$Day_of_a_Week,levels = c("Sunday", 
                                                                        "Monday", 
                                                                        "Tuesday", 
                                                                        "Wednesday", 
                                                                        "Thursday", 
                                                                        "Friday",
                                                                        "Saturday"))
average_count_per_day <- average_count_per_day %>%
  arrange(Day_of_a_Week)
chartJSRadar(average_count_per_day,
             main = 'Average words per day',
             showLegend = FALSE,
             polyAlpha = 0.2,
             lineAlpha = 5)
```


```{r echo=FALSE,warning=FALSE}
number_of_msg_per_day <- as.data.frame(select(df,date) %>%count(date))
#print(paste('Average number of messages sent per day :',round(mean(number_of_msg_per_day$n))))

```

Average Number of Messages sent per day **`r round(mean(number_of_msg_per_day$n))`**
  
```{r echo=FALSE,warning=FALSE}
for(i in 1:dim(chat_participants)[1]){
  cat <- df %>% 
    filter(author == as.character(chat_participants[i,])) %>% 
    count(date) %>%
    summarise(mean(n))
  print(paste('Average number of text sent by',chat_participants$author[i],'per day is',round(cat$`mean(n)`[1])))
  
}

```


```{r echo=FALSE,warning=FALSE}
max_msg_on <- as.data.frame(select(df,date) %>%count(date) %>%
                              arrange(desc(n)) %>% head(1))
min_msg_on <- as.data.frame(select(df,date) %>%count(date) %>%
                              arrange(desc(n)) %>% tail(1))
#print(paste('Maximum number of message sent was ', max_msg_on$n[1],'on',max_msg_on$date[1]))
#print(paste('Minimum number of message sent was ', min_msg_on$n[1],'on',min_msg_on$date[1]))
```

Maximum number of message sent was **`r max_msg_on$n[1]`** on **`r max_msg_on$date[1]`**
  
  Minimum number of message sent was **`r min_msg_on$n[1]`** on **`r min_msg_on$date[1]`**
  
  **Maximum number of messages by each person**
```{r echo=FALSE,warning=FALSE}
for(i in 1:dim(chat_participants)[1]){
  cat <- df %>% 
    filter(author == as.character(chat_participants[i,])) %>% 
    count(date) %>%
    arrange(desc(n))
  print(paste('maximum number of text sent by',chat_participants$author[i],'is',cat$n[i],"on",cat$date[i]))
  
}
```

**Average Number of Messages Per Hour can be found from below graph**
  
```{r echo=FALSE,warning=FALSE}
hourly_msg <- df %>%
  select(hour,date)%>%
  count(hour,date) %>%
  group_by(hour)%>%
  summarise(round(a_mean = mean(n)))%>%
  arrange(desc(-hour)) 
colnames(hourly_msg) <- c('Hours_in_a_day','Average_Number_Of_Messages')
#hourly_msg

pl <- ggplot(hourly_msg,aes(x=Hours_in_a_day,y=Average_Number_Of_Messages)) +
  geom_bar(stat='identity',fill = 'pink',colour ='black' )+ theme(legend.position = "none") +
  ggtitle('Average Messages Per Hour')


ggplotly(pl)

```
```{r echo=FALSE,warning=FALSE}
max_msg <- function(data) sapply(data, max,na.rm=TRUE)
#print(paste('The busiest hour is',
# hourly_msg %>%
#  arrange(desc(Average_Number_Of_Messages)) %>% 
# head(1) %>% 
# select(Hours_in_a_day),'with',
#max_msg(df %>%
#      select(hour,date)%>%
#     count(hour,date) %>%
#    group_by(hour)%>%
#   summarise(a_mean = round(mean(n)))%>%
#    arrange(desc(-hour)) %>% select(a_mean)),'average messages'))

```

From the above Graph we can see the busies Hour is **`r hourly_msg %>% arrange(desc(Average_Number_Of_Messages)) %>%head(1) %>% select(Hours_in_a_day)`** with **`r max_msg(df %>%select(hour,date)%>% count(hour,date) %>% group_by(hour) %>% summarise(a_mean = round(mean(n))) %>% arrange(desc(-hour)) %>% select(a_mean))`** average messages

```{r echo=FALSE,warning=FALSE}
cloud_tweet <- df
cloud_tweet$text <- iconv(cloud_tweet$text, from = 'UTF-8', to = 'ASCII//TRANSLIT')

corpus <- VCorpus(VectorSource(cloud_tweet$text))
#as.character(corpus[[33]])
removeURL <- content_transformer(function(x) gsub("(f|ht)tp(s?)://\\S+", "", x, perl=T))
corpus <- tm_map(corpus, removeURL)
#as.character(corpus[[33]])
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
corpus <- tm_map(corpus, toSpace, "/")
#as.character(corpus[[33]])
corpus <- tm_map(corpus, toSpace, "@")
#as.character(corpus[[46]])
corpus <- tm_map(corpus, toSpace, "\\|")
#as.character(corpus[[33]])
to_corpus <- tm_map(corpus, toSpace, "\\|")
corpus <- tm_map(corpus,removeWords, stopwords())
corpus <- tm_map(corpus,content_transformer(tolower))
#as.character(corpus[[1]])
corpus <- tm_map(corpus,removeWords, c('dha','media','omitted'))
corpus <- tm_map(corpus,removePunctuation)
#as.character(corpus[[1]])
corpus <- tm_map(corpus,removeNumbers)
#as.character(corpus[[3]])
#as.character(corpus[[1]])
corpus <- tm_map(corpus,stripWhitespace)
#as.character(corpus[[1]])
cleaned_text <-data.frame(text=unlist(sapply(corpus, `[`, "content")), stringsAsFactors=F)

cleaned_text$author <- df$author
dtm <- TermDocumentMatrix(corpus)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
rownames(d) <- c()
colnames(d) <- c('Word','Occurance')
#print('most used words are')
#print(head(d, 10))

```
**The Most Used Words are**
```{r echo=FALSE,warning=FALSE}
top10 <- head(d, 10)
knitr :: kable(top10)
```

# **The WordCloud **
## greater the size, greater the word used
```{r echo=FALSE,warning=FALSE}
pal <- brewer.pal(12,'Set3')
#wordcloud(corpus, min.freq = 100, max.words = Inf,width =1000,heigt = 1000,random.order = FALSE,colors = pal)
wordcloud2(d, size = 1.5)
```






**TOP 10 Words used by each person**
  
  
```{r echo=FALSE,warning=FALSE}
for(i in 1:dim(chat_participants)[1]){
  cleaned_text %>%
    filter(author == chat_participants[i,]) %>%
    select(text)
  corpus <- VCorpus(VectorSource(cleaned_text %>%
                                   filter(author == chat_participants[i,]) %>%
                                   select(text)))
  dtm <- TermDocumentMatrix(corpus)
  m <- as.matrix(dtm)
  v <- sort(rowSums(m),decreasing=TRUE)
  d <- data.frame(word = names(v),freq=v)
  rownames(d)<-c()
  d$percentage <- round(d$freq/sum(d$freq)*100,2)
  print(paste('top ten words used by',
              chat_participants[i,],':'))
  colnames(d) <- c('Word','Occurance','Percentage')
  print(head(d, 5))
  
  print(paste('the most used word by',
              chat_participants[i,],'is : ',head(d,5)[1,1]))
}
```



**The most Used emorji**
  
```{r echo=FALSE,warning=FALSE}
emoji_data <- rwhatsapp::emojis %>% # data built into package
  mutate(hex_runes1 = gsub("\\s[[:alnum:]]+", "", hex_runes)) %>% # ignore combined emojis
  mutate(emoji_url = paste0("https://abs.twimg.com/emoji/v2/72x72/", 
                            tolower(hex_runes1), ".png"))
pl1<- chat %>%
  unnest(emoji) %>%
  count(emoji, sort = TRUE) %>%
  top_n(n = 6, n) %>%
  left_join(emoji_data, by = "emoji") %>%
  ggplot(aes(x = reorder(emoji, n), y = n, fill = emoji)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  geom_image(aes(y = n + 20, image = emoji_url)) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
pl2 <- chat %>%
  unnest(emoji) %>%
  count(author, emoji, sort = TRUE) %>%
  group_by(author) %>%
  top_n(n = 6, n) %>%
  left_join(emoji_data, by = "emoji") %>% 
  ggplot(aes(x = reorder(emoji, n), y = n, fill = author)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  geom_image(aes(y = n + 20, image = emoji_url)) +
  facet_wrap(~author, ncol = 2, scales = "free_y") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
pl1  
pl2

```


# Thank You
